A memory frontier for complex synapses

### 2013-05-30 NIPS/SynapseNIPS.tex
added supp

@@

>>>>

In terms of these quantities, the area can be written as
%
\begin{equation}\label{eq:areaEta}
\begin{aligned}
  A &= \sqrt{N}(4f\pot f\dep) \sum_{ij} \eq_i \prn{\M\pot_{ij}-\M\dep_{ij}} \prn{\eta^+_i-\eta^+_j}\\
    &= \sqrt{N}(4f\pot f\dep) \sum_{ij} \eq_i \prn{\M\pot_{ij}-\M\dep_{ij}} \prn{\eta^-_j-\eta^-_i}.
\end{aligned}
\end{equation}
%

@@

We have developed a general theory of learning and memory with complex synapses, allowing for an exploration of the entire space of models.
If we are to understand the wealth of data that is arriving regarding the molecular mechanisms of synaptic plasticity \cite{Bliss1993LTP,Bredt2003AMPA,Coba2009phosphorylation}, we will need more of this exploration so that we can build an understanding of the relation between structure and function.

We have begun this exploration by finding upper bounds on the memory storage of these synapses.
